Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-09-08 paper/paper.tex
work on getting contour plots unified (incomplete) Tested everything on bennet.

\begin{figure*}
  \includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/image-plot}
  \includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/single-image-plot}
  \caption{\fixme{We should figure out units and use the same levels
      as in the main plot.  I also want to figure out why the two
      plots look different, and make them the same size.  Can we just
      do the gaussian} Contour plot images of the concentration of each protein
    species in a natural pill-shaped bacterium at regular intervals in
    time (one second intervals), with darker regions indicating higher
    concentration. The upper plots shows results from the
    deterministic simulation and the lower shows results from the
    stochastic simulation.  The cells pictured are $4\micron$ in
    length, measured from end to end.  The order of frames is such
    that individual MinD proteins begin at the bottom of the plot (in
    the MinD:ATP state in the cytoplasm), and progress upward until
    they reach the MinE:MinD:ATP membrane-bound complex.  At that
    point, they will spontaneously dissociate into cytoplasmic MinE
    (the top row) and the starting state of cytoplasmic MinD:ADP.  The
    densities plotted are integrated along the axis orthogonal to the
    page, and the color scale is chosen separately for each species
    with black as the maximum value over space and time.  The
    stochastic densities are smeared out over space using a guassians
    approximation developed by Zhang et all~\cite{zhang2007gaussian}}.
  \label{image-p}
\end{figure*}

@@

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{../paper/plot-ave}
  \caption{\fixme{Look into unifying the color scale, and adding a
      scale bar.} Arrows depicting global maxima in space and local
    maxima in
    time overlayed on color plots of time averaged total MinD density.
    A density threshold is chosen and only maxima above this threshold
    are shown. The plots serve to illistrate what is observed in our
    movies.  The simulation time covered in these is 1000 seconds
    \fixme{this is not true yet - need to change the data once its
      finished right now 2 of them are 1000 the others are like 980}.
    The top row shows plots published by Mannik of the MinD maxima
    behavoir and the bottom two rows show our pancake shapes that are
    designed to have the same shape.  The middle row shows results
    from the stochastic simulation and the bottom shows results from
    the deterministic.  We can see that the stochastic method shows
    behavoir that is similar to experiment while the deterministic
    method shows maximization that is too regular and robust.}
  \label{randst-plot-ave}
\end{figure*}

>>>>

\begin{figure*}
  \includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/image-plot}
  %\includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/single-image-plot}
  \includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/single-image-plot}
  \caption{\fixme{We should figure out units and use the same levels
      as in the main plot.  I also want to figure out why the two
      plots look different, and make them the same size.  Can we just
      do the gaussian} Contour plot images of the concentration of each protein
    species in a natural pill-shaped bacterium at regular intervals in
    time (one second intervals), with darker regions indicating higher
    concentration. The upper plots shows results from the
    deterministic simulation and the lower shows results from the
    stochastic simulation.  The cells pictured are $4\micron$ in
    length, measured from end to end.  The order of frames is such
    that individual MinD proteins begin at the bottom of the plot (in
    the MinD:ATP state in the cytoplasm), and progress upward until
    they reach the MinE:MinD:ATP membrane-bound complex.  At that
    point, they will spontaneously dissociate into cytoplasmic MinE
    (the top row) and the starting state of cytoplasmic MinD:ADP.  The
    densities plotted are integrated along the axis orthogonal to the
    page, and the color scale is chosen separately for each species
    with black as the maximum value over space and time.  The
    stochastic densities are smeared out over space using a guassians
    approximation developed by Zhang et all~\cite{zhang2007gaussian}}.
  \label{image-p}
\end{figure*}

@@

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{../paper/plot-ave}
  \caption{Arrows depicting global maxima in space and local
    maxima in
    time overlayed on color plots of time averaged total MinD density.
    A density threshold is chosen and only maxima above this threshold
    are shown. The plots serve to illistrate what is observed in our
    movies.  The simulation time covered in these is 1000 seconds
    \fixme{this is not true yet - need to change the data once its
      finished right now 2 of them are 1000 the others are like 980}.
    The top row shows plots published by Mannik of the MinD maxima
    behavoir and the bottom two rows show our pancake shapes that are
    designed to have the same shape.  The middle row shows results
    from the stochastic simulation and the bottom shows results from
    the deterministic.  We can see that the stochastic method shows
    behavoir that is similar to experiment while the deterministic
    method shows maximization that is too regular and robust.}
  \label{randst-plot-ave}
\end{figure*}
